Test data

### 2022-07-22 Shiny/Test/Flexdashboard rows.Rmd
Facet test. Plot and KPI fixes.

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using fontawesome for more up-to-date fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())

@@

### KPI
```{r}
valueBoxOutput("KPI_box_admin")
```

### KPI 2
```{r}
valueBoxOutput("KPI_box_fundraising")
```

### KPI 3
```{r}
valueBoxOutput("KPI_box_OPX")
```

### KPI 4
```{r}
valueBoxOutput("KPI_box_private")
```

### KPI 5
```{r}
valueBoxOutput("KPI_box5")
```

@@

@@

  # Creating KPI_admin value
  KPI_admin_num <- reactive({
    exceldata() |>
      # most recent year
      filter(year == max(year)) |>
      # Calculating the value as a percentage; removing all other
      transmute(
        KPI_admin = expenses_administrative / (expenses_program_services +
          expenses_administrative +
          expenses_fundraising +
          expenses_other) * 100
      ) |>
      # just want the single number
      pull()
  })

@@

  # Creating OPX KPI
  KPI_OPX_num <- reactive({
    exceldata() |>
      filter(year == max(year)) |>
      transmute(
        KPI_OPX = (revenue_private_contributions + revenue_investments +
          assets_cash_in_bank_and_cash_equivalents) /
          (liability_short_term_grants_payable +
            liability_revocable_endowments +
            liability_long_term_grants_payable) * 100
      ) |>
      pull()
  })

  # Creating private donations growth
  KPI_private_num <- reactive({
    exceldata() |>
      transmute(
        growth = revenue_private_contributions[1] / revenue_private_contributions[2] * 100
      ) |>
      pull() |>
      first()
  })

  # Creating public grants growth
  KPI_public_num <- reactive({
    exceldata() |>
      transmute(
        growth = revenue_public_grants[1] / revenue_public_grants[2] * 100
      ) |>
      pull() |>
      first()
  })

  # Creating the value box for administrative expenses
  output$KPI_box_admin <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_admin_num()),
      caption = "Administration as a % of total expenses",
      color = "primary",
      icon = "fa-random"
    )
  })

  # Creating value box for fundraising ROI
  # Unsure about colour levels
  output$KPI_box_fundraising <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_fundraising_num()),
      caption = "Fundraising ROI",

      # Colour depends on value
      color = if (KPI_fundraising_num() < 100) {
        "danger"
      } else if (KPI_fundraising_num() < 200) {
        "warning"
      } else {
        "success"
      },
      icon = "fas fa-donate"
    )
  })

  # KPI_OPX
  output$KPI_box_OPX <- renderValueBox({
    valueBox(
      value = str_c(format(KPI_OPX_num(), digits = 3), "%"),
      caption = "Liquid assets / obligations",
      color = ifelse(KPI_OPX_num() <= 100, "success", "danger"),
      icon = "fas fa-seedling"
    )
  })

  # Creating value box for public grants growth
  output$KPI_box_private <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_private_num()),
      caption = "Private donation growth",
      color = ifelse(KPI_private_num() < 100, "warning", "success"),
      icon = "fas fa-hands-helping"
    )
  })

  output$KPI_box5 <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_public_num()),
      caption = "Public grants growth",
      color = ifelse(KPI_public_num() < 100, "warning", "success"),
      icon = "fas fa-hand-holding-usd"
    )
  })

@@

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |>
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year = as.factor(year),
        Other = expenses_other,
        Administrative = expenses_administrative,
        Fundraising = expenses_fundraising,
        `Program services` = expenses_program_services
      ) |>
      # Pivoting to use fill
      pivot_longer(c(Other:`Program services`), names_to = "Expenses") |>
      # Ordering for the plot
      mutate(
        Expenses = ordered(Expenses,
          levels =
            c("Program services", "Other", "Fundraising", "Administrative")
        )
      ) |>
      ggplot(aes(Year, value, fill = Expenses)) +
      geom_col() +
      # Flipping, because the Excel file only contains two years atm
      coord_flip() +
      currency_scale() +
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(x = "", y = "", title = "Expenses (in thousands)")
  })

  output$expenses_plotly <- renderPlotly(
    ggplotly(expenses_plot()) |>
      layout(
        annotations =
          plotly_caption()
      )
  )

@@

# Function to turn KPI values into NA or percentage string
KPI_to_string <- function(variable){
  # Returning NA if the KPI is Inf (division by zero) or NA, to avoid
  # layout-breaking errors, otherwise formatting
  if (is.na(variable)){
    NA
  } else if (variable == Inf){
    NA
  } else {
    # Shortening (lengthening) the value, adding %
    str_c(format(variable, digits = 3), "%")
  }
}

>>>>

```{r setup, include=FALSE}
# Loading packages using pacman to ensure they're all installed
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(
  shiny, tidyverse, scales, rvest, janitor, plotly, readxl,
  flexdashboard, MetBrewer, fontawesome, htmltools
)
# Using fontawesome for more up-to-date (and currently supported) fontawesome icons
htmltools::tagList(fontawesome::fa_html_dependency())

@@

### KPI Fundraising
```{r}
valueBoxOutput("KPI_box_fundraising")
```

### KPI OPX
```{r}
valueBoxOutput("KPI_box_OPX")
```

### KPI Private growth
```{r}
valueBoxOutput("KPI_box_private")
```

### KPI Public growth
```{r}
valueBoxOutput("KPI_box_public")
```

### KPI Private/public proportion
```{r}
valueBoxOutput("KPI_box_proportion")
```

@@

### Revenues
```{r}
plotlyOutput("revenue_plotly")
```

@@

@@

  # Creating OPX KPI
  KPI_OPX_num <- reactive({
    exceldata() |>
      # most recent year
      filter(year == max(year)) |>
      # Calculating the value as a %
      transmute(
        KPI_OPX = (revenue_private_contributions + revenue_investments +
          assets_cash_in_bank_and_cash_equivalents) /
          (liability_short_term_grants_payable +
            liability_revocable_endowments +
            liability_long_term_grants_payable) * 100
      ) |>
      # Just the single number
      pull() |> 
      first()
  })

  # Creating private donations growth
  KPI_private_num <- reactive({
    exceldata() |>
      # Calculating the two most recent years as a %
      transmute(
        growth = revenue_private_contributions[1] / revenue_private_contributions[2] * 100
      ) |>
      # Pulling the first instance of the number
      pull() |>
      first()
  })

  # Creating public grants growth
  KPI_public_num <- reactive({
    exceldata() |>
      # Calculating the two most recent years as a %
      transmute(
        growth = revenue_public_grants[1] / revenue_public_grants[2] * 100
      ) |>
      # Pulling the first instance of the number
      pull() |>
      first()
  })

  # Creating public/private proportion
  KPI_proportion <- reactive({
    exceldata() |> 
    transmute(
    proportion = (revenue_private_contributions + revenue_membership_fees) / (revenue_public_grants + revenue_private_contributions + revenue_membership_fees) * 100
  ) |> 
  pull() |> 
  first()
  })

  # Creating value box for fundraising ROI
  # Unsure about colour levels
  output$KPI_box_fundraising <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_fundraising_num()),
      caption = "Fundraising ROI",
      # Colour depends on value
      color = if (is.na(KPI_fundraising_num())) {
        "primary"
      } else if (KPI_fundraising_num() < 100) {
        "danger"
      } else if (KPI_fundraising_num() < 200) {
        "warning"
      } else {
        "success"
      },
      icon = "fas fa-donate"
    )
  })

  # KPI_OPX
  output$KPI_box_OPX <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_OPX_num()),
      caption = "Liquid assets / obligations",
      color = if (is.na(KPI_OPX_num())) {
        "primary"
      } else if (KPI_OPX_num() < 100) {
        "warning"
      } else {
        "success"
      },
      icon = "fas fa-seedling"
    )
  })

  # Creating value box for private donations growth
  output$KPI_box_private <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_private_num()),
      caption = "Private donation growth",
      color = if (is.na(KPI_private_num())){
        "primary"
      } else if (KPI_private_num() < 100){
        "warning"
      } else {
        "success"
      },
      icon = "fas fa-hands-helping"
    )
  })

  # Creating value box for public grants growth
  output$KPI_box_public <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_public_num()),
      caption = "Public grants growth",
      color = if (is.na(KPI_public_num())){
        "primary"
      } else if (KPI_public_num() < 100){
        "warning"
      } else {
        "success"
      },
      icon = "fas fa-hand-holding-usd"
    )
  })

  # Creating value box for private/public proportion
  output$KPI_box_proportion <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_proportion()),
      caption = "Private donations",
      color = "info",
      icon = "fas fa-percentage"
    )
  })

@@

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |>
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year = as.factor(year),
        Other = expenses_other,
        Administrative = expenses_administrative,
        Fundraising = expenses_fundraising,
        `Program services` = expenses_program_services
      ) |>
      # Pivoting to use fill
      pivot_longer(c(Other:`Program services`), names_to = "Expenses") |>
      # Ordering for the plot
      mutate(
        Expenses = ordered(Expenses,
          levels =
            c("Program services", "Other", "Fundraising", "Administrative")
        )
      ) |>
      ggplot(aes(Year, value, fill = Expenses)) +
      geom_col() +
      scale_y_continuous(labels = label_dollar(prefix = "NOK ")) +
      scale_fill_met_d("Hokusai2") +
      labs(x = "", y = "", title = "Expenses (in thousands)")
  })

  output$expenses_plotly <- renderPlotly(
    ggplotly(expenses_plot())
  )

  #----Revenue------------------------------------------
  revenue_plot <- reactive({
    exceldata() |> 
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year                    = as.factor(year),
        `Private contributions` = revenue_private_contributions,
        `Membership fees`       = revenue_membership_fees,
        `Public grants`         = revenue_public_grants,
        Investments             = revenue_investments,
        `Operational activities`= revenue_operational_activities,
        `Commercial activities` = revenue_commercial_activities,
        Other                   = revenue_other
      ) |> 
      # Pivoting to use fill
      pivot_longer(
        c(`Private contributions`:Other), names_to = "Revenue source"
      ) |> 
      ggplot(aes(Year, value, fill = `Revenue source`)) +
      geom_col() +
      scale_y_continuous(labels = label_dollar(prefix = "NOK ")) +
      scale_fill_manual(values = met.brewer("Hokusai2", 7)) +
      labs(x = "", y = "", title = "Revenue (in thousands)")
  })

  output$revenue_plotly <- renderPlotly(
    ggplotly(revenue_plot())
  )

@@

# Function to turn KPI values into NA or percentage string
KPI_to_string <- function(variable){
  # Returning NA if the KPI is Inf (division by zero) or NA, to avoid
  # layout-breaking errors, otherwise formatting
  if (is.na(variable)) {
    NA
  } else if (variable == Inf) {
    NA
  } else {
    # Shortening (lengthening) the value, adding %
    str_c(format(variable, digits = 3), "%")
  }
}
```

### 2022-07-22 Shiny/Test/Test data.Rmd
Facet test. Plot and KPI fixes.

@@

### Private/public
```{r}
kreft_excel |> 
  transmute(
    proportion = revenue_private_contributions / revenue_public_grants * 100
  ) |> 
  pull() |> 
  first()
```

@@

kreft_excel |> 
  filter(year == max(year)) |> 
      transmute(
        KPI_OPX = (revenue_private_contributions + revenue_investments +
                 assets_cash_in_bank_and_cash_equivalents) /
      (liability_short_term_grants_payable +
         liability_revocable_endowments +
         liability_long_term_grants_payable) * 100
      ) |> 
      pull()
```

>>>>

kreft_excel |> 
      filter(year == max(year)) |>
      transmute(
        # Calculating the value as a percentage; removing all other
        KPI_fundraising_num =
          (revenue_private_contributions +
            revenue_membership_fees - expenses_fundraising) /
            expenses_fundraising * 100
      ) |>
      # just want the single number
      pull()

@@

### Private/public
```{r}
kreft_excel |> 
  transmute(
    proportion = (revenue_private_contributions + revenue_membership_fees) / (revenue_public_grants + revenue_private_contributions + revenue_membership_fees) * 100
  ) |> 
  pull() |> 
  first()

kreft_excel
```

@@

kreft_excel |> 
  filter(year == max(year)) |> 
      transmute(
        KPI_OPX = (revenue_private_contributions + revenue_investments +
                 assets_cash_in_bank_and_cash_equivalents) /
      (liability_short_term_grants_payable +
         liability_revocable_endowments +
         liability_long_term_grants_payable) * 100
      ) |> 
      pull()
kreft_excel |> 
filter(year == max(year)) |>
      # Calculating the value as a %
      transmute(
        KPI_OPX = (revenue_private_contributions + revenue_investments +
          assets_cash_in_bank_and_cash_equivalents) /
          (liability_short_term_grants_payable +
            liability_revocable_endowments +
            liability_long_term_grants_payable) * 100
      ) |>
      # Just the single number
      pull()
```

### Revenue plot
```{r}
kreft_excel |> 
  transmute(
        Year                    = as.factor(year),
        `Private contributions` = revenue_private_contributions,
        `Membership fees`       = revenue_membership_fees,
        `Public grants`         = revenue_public_grants,
        Investments             = revenue_investments,
        `Operational activities`= revenue_operational_activities,
        `Commercial activities` = revenue_commercial_activities,
        Other                   = revenue_other
      ) |> 
      # Pivoting to use fill
      pivot_longer(
        c(`Private contributions`:Other), names_to = "Revenue source"
      ) |> 
      ggplot(aes(Year, value, fill = `Revenue source`)) +
      geom_col() +
      # Flipping, because the Excel file only contains two years atm
      coord_flip() +
      scale_fill_met_d("Hokusai2", direction = -1) +
      labs(x = "", y = "", title = "Revenue (in thousands)")
```
